\documentclass{scrartcl}
\usepackage[lmargin=1.5cm, rmargin=2.5cm, tmargin=1.5cm, bmargin=1.5cm, noheadfoot]{geometry}
\usepackage{parcolumns}
\usepackage{lipsum}
\usepackage[mathscr]{euscript}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{textcomp}

\usepackage{fontspec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine}

%fix the links so they are both printable and clickable.
\usepackage{hyperref}
\hypersetup{
   colorlinks,
   citecolor=black,
   filecolor=black,
   linkcolor=black,
   urlcolor=blue
}
\urlstyle{same}

\usepackage{multirow}
\begin{document}
\setlength{\parindent}{0pt}
\setlength{\parskip}{\baselineskip}
\setlength{\parsep}{0in}
\pagestyle{empty}

\newcommand{\expert}[1]{\mdseries\itshape{#1}}
\newcommand{\citembullet}{$\diamond$}

\begin{center}
\begin{tabular}{c|c|c}
\multicolumn{3}{c}{{\sc\bfseries\Huge Jason Michael Switzer}}\tabularnewline
Software Engineer & \href{mailto:jswitzer@gmail.com}{jswitzer@gmail.com} & \href{http://www.voidreturn.com}{voidreturn.com}\tabularnewline
\end{tabular}
\end{center}

\fontencoding{OT1}\fontfamily{ptm}%
\fontsize{11}{12}\selectfont
\par \
\begin{parcolumns}[rulebetween=false,colwidths={1=.12\linewidth,3=0.08\linewidth},nofirstindent]{3}
\colchunk[1]{\sc\bfseries Qualification\\Summary}
\colchunk[2]{%
A highly motivated and detailed Software Engineer with a wide range of knowledge and capabilities. Master level knowledge of machine learning, intelligent systems, scalable distributed systems, multi-threaded environments, dead-lock avoidance, user interface design, and object oriented design patterns, and defect containment. Experienced in all aspects of the development life-cycle, including project estimation, design, implementation, documentation, regression unit testing, deployment, and legacy maintenance.
\\

{\em Areas of expertise include:}
\begin{itemize}
   \item Machine Learning.
   \item User Interface Design \& Implementation.
   \item High Performance Computing.
   \item Code Analysis and Optimization.
   \item Multi-tier Enterprise Application Design \& Implementation.
   \item Passionate and dedicated to the art of software engineering. Flexible, quick learner, and team player.
\end{itemize}
\par \
}
\colplacechunks
\colchunk[1]{{\sc\bfseries Technical\\Skills}\\ \\ {\expert denotes \\ specialty}}
\colchunk[2]{%
\setlength{\parskip}{0pt}
\vspace{-\baselineskip}
\begin{itemize}[font=\sffamily\bf, leftmargin=1.9cm, topsep=0cm, style=nextline]
\item[Languages] {\expert C}, {\expert C++}, {\expert Perl}, {\expert Java (1.4+)}, Markup (XML, HTML), \LaTeX, SQL, Python, C\#, Assembly (MIPS), Lua, ASP.Net, UML.
\item[Theory] {\expert Qt}, Motif, Xlib, GTK+, {\expert boost}, {\expert pthreads}, OpenMP, MPI, .NET, JDK, {\expert Coverity}, JUnit, {\expert RMI}, {\expert Perl \& CPAN}, Perl/Tk, libogg, libflac, {\expert JNI}, {\expert POSIX}, J2EE, libpcap, cmake, Mudflap.
\item[Toolkits] {\expert Network programming}, {\expert Multi-threadeding}, Security analysis, detection and prevention, Linux kernel module development, {\expert Linux / POSIX compliance}, {\expert Model-View-Controller design}, {\expert Machine learning / data mining}, {\expert Natural Language Processing}, {\expert Statistical reasoning}, {\expert Object-oriented design patterns}, Stenography, Regression \& unit testing, {\expert Technical documentation}, {\expert Debugging tools (gdb, valgrind, etc)}, {\expert CMMI development lifecycle}, {\expert Defect containment \& prevention}.
\end{itemize}
\setlength{\parskip}{\baselineskip}
\par \
}
\colplacechunks
\colchunk[1]{\sc\bfseries Education}
\colchunk[2]{%
\setlength{\parskip}{0pt}
\vspace{-\baselineskip}
\begin{itemize}[font=\sffamily\bf, leftmargin=0cm, topsep=0cm, partopsep=0cm, listparindent=0cm, style=nextline]
\item[\textbullet] University of Texas at Dallas\\
M.Sc. in Computer Science - Intelligent Systems Track\\
Thesis: {\em Semi-supervised Subjectivity Classification and Application to Jargon Heavy Corpora.}
\end{itemize}
\par \ 
}
\colchunk[3]{\it\small December 2010}
\colplacechunks
\colchunk[2]{%
\setlength{\parskip}{0pt}
\vspace{-\baselineskip}
\begin{itemize}[font=\sffamily\bf, leftmargin=0cm, topsep=0cm, partopsep=0cm, listparindent=0cm, style=nextline]
\item[\textbullet] University of Texas at San Antonio\\
B.Sc. in Computer Science\\
College of Sciences Dean's List: Fall 2003. Honor Roll: Spring 2004
\end{itemize}
\setlength{\parskip}{\baselineskip}
\par \
}
\colchunk[3]{\it\small August 2005}
\colplacechunks
\colchunk[1]{\sc\bfseries Experience}
\colchunk[2]{%
{\bf Senior Software Engineer}\\
L-3 Communications -- Mission Integration Systems\\
\begin{itemize}
\item Core developer on the Tactical Reconnaissance platform (over 3 million SLOC). Operator workstation responsible for interfacing directly and indirectly to all hardware on the aircraft.
\item Developer on wide variety of products, including operator workstation, high speed recording platform (patent pending), signal analysis platform, optics recording platform, and COTS bench test system.
\item Collaborate with a large team and a code-base focusing on Human/Computer Interaction data collection and analysis products.
\item Architect of a new Java/JNI development toolkit bridging the vast legacy code-base, allowing for the network centric control platforms connecting airborne platforms to ground-based systems.
\item Member of the charter team leading CMMI Level 5 compliance.
\item Spearheaded company-wide defect containment compliance via Coverity static analysis and unit/functional testing.
%FIXME need to gather real metrics
%\item Reduced defect density by FIXME\% yearly. Reduced out-of-phase defects by FIXME\% yearly.
\par \
\end{itemize}
}
\colchunk[3]{\it\small 2005 - present}
\colplacechunks
\colchunk[2]{%
{\bf System Analyst}\\
Secorp Technologies\\
\begin{itemize} 
\item Designed and implemented multi-tiered enterprise-level applications.
\item Project Lead for a small team -- responsible for primary technical decisions.
\item Designed, developed, and maintained a custom data access layer above ADO.NET.
\item Initiated project transition to C\# and the .NET Architecture.
\end{itemize}
\par \
}
\colchunk[3]{\it\small 2003 - 2005}
\colplacechunks
\colchunk[1]{\bfseries Publication}
\colchunk[2]{%
\setlength{\parskip}{0pt}
\vspace{-\baselineskip}
\begin{itemize}[font=\sffamily\bf, leftmargin=0cm, topsep=0cm, partopsep=0cm, listparindent=0cm, style=nextline]
\item[\textbullet] Switzer, Jason, Latifur Khan, Fahad Bin Muhaya. 2011. {\it Subjectivity Classification and Analysis of the ASRS Corpus.} In IEEE Society of Information Reuse and Integration, pages 136-141.\\
Full Text: \url{http://www.voidreturn.com/pubs/IEEE\_IRI.pdf}.
\par \
\end{itemize}
}
\colchunk[3]{\it\small August 2011}
\colplacechunks
\colchunk[2]{%
\setlength{\parskip}{0pt}
\vspace{-\baselineskip}
\begin{itemize}[font=\sffamily\bf, leftmargin=0cm, topsep=0cm, partopsep=0cm, listparindent=0cm, style=nextline]
\item[\textbullet] Semi-supervised Subjectivity Classification and Application to Jargon Heavy Corpora\\
Full Text: \url{http://www.voidreturn.com/pubs/SSCaAJHC.pdf}.\\
Abstract: \url{http://www.voidreturn.com/pubs/SSCaAJHC\_Abstract.pdf}.
\end{itemize}
%\setlength{\parskip}{\baselineskip}
\par \
}
\colchunk[3]{\it\small December 2010}
\colplacechunks
\colchunk[1]{\bfseries Research}
\colchunk[2]{%
\setlength{\parskip}{0pt}
\vspace{-\baselineskip}
\begin{itemize}[font=\sffamily\bf, leftmargin=0cm, topsep=0cm, partopsep=0cm, listparindent=0cm, style=nextline]
\item[\textbullet] {\it Thesis:} Semi-supervised Subjectivity Classification and Application to Jargon Heavy Corpora.\\
{\it Advisor:} Dr. Latifur Khan.\\
{\it Topic:} Natural Language Processing, Clustering, Subjectivity Classification, WordNet.
\par \
\end{itemize}
}
\colchunk[3]{\it\small Fall 2010}
\colplacechunks
\colchunk[2]{%
\setlength{\parskip}{0pt}
\vspace{-\baselineskip}
\begin{itemize}[font=\sffamily\bf, leftmargin=0cm, topsep=0cm, partopsep=0cm, listparindent=0cm, style=nextline]
\item[\textbullet] Semi-supervised Subjectivity Classification and Application to Jargon Heavy Corpora.\\
Full Text: \url{http://www.voidreturn.com/pubs/SSCaAJHC.pdf}.\\
Abstract: \url{http://www.voidreturn.com/pubs/SSCaAJHC\_Abstract.pdf}.
\par \
\end{itemize}
}
\colchunk[3]{\it\small Submitted Fall 2010}
\colplacechunks
\colchunk[2]{%
\setlength{\parskip}{0pt}
\vspace{-\baselineskip}
\begin{itemize}[font=\sffamily\bf, leftmargin=0cm, topsep=0cm, partopsep=0cm, listparindent=0cm, style=nextline]
\item[\textbullet] {\it Independent Study:} Parallelization of Sparse Matrix Multiplication\\
{\it Advisor:} Dr. Rajendra V. Boppana\\
{\it Uncredited publication:} E. Brookes, R. V. Boppana and B. Demeler, Computing Large Sparse Multivariate Optimization Problems with an Application in Biophysics, Supercomputing, Nov. 2006.
\par \ 
\end{itemize}
}
\colchunk[3]{\it\small Spring 2004}
\colplacechunks
\colchunk[2]{%
\setlength{\parskip}{0pt}
\vspace{-\baselineskip}
\begin{itemize}[font=\sffamily\bf, leftmargin=0cm, topsep=0cm, partopsep=0cm, listparindent=0cm, style=nextline]
\item[\textbullet] {\it Independent Study:} Micro-kernels and the ZINC Linux Kernel Automatic Security System\\
{\it Advisor:} Dr. Hugh Maynard\\
\end{itemize}
%\setlength{\parskip}{\baselineskip}
}
\colchunk[3]{\it\small Fall 2003}
\colplacechunks
\colchunk[1]{\sc\bfseries Research\\Interests}
\colchunk[2]{%
Machine learning, statistical pattern recognition, natural language processing, intelligent systems, data \& text mining.
\par \ }
\colplacechunks
\colchunk[1]{\sc\bfseries Clearance}
\colchunk[2]{%
{\bf Top Secret} -- Department of Defense\\
SI/TK -- Big Safari Access
\par \ }
\colchunk[3]{\it\small 2008 - 2013}
\colplacechunks
\colchunk[1]{\sc\bfseries Certification}
\colchunk[2]{%
Red Hat Certified System Administrator, RHEL 5
\par \ }
\colchunk[3]{\it\small Fall 2010}
\colplacechunks
\colchunk[1]{\sc\bfseries Open Source}
\colchunk[2]{%
GitHub account: \url{http://www.github.com/s1n}
%FIXME don't put the \par on the last item
}
\colplacechunks
\end{parcolumns}
\end{document}